%
% Resume
% Contents
%


% Header
\fancyhead{} % clear default header

\fancyhead[C]{\Large{\textbf{Zhu Zhanyan}}\\
              \normalsize{Data Engineer}}
\fancyhead[L]{\href{mailto:mrzzy.dev@gmail.com}{mrzzy.dev@gmail.com}\\}
\fancyhead[R]{
  \href{https://github.com/mrzzy}{github.com/mrzzy} \\
  \href{https://linkedin.com/in/zhu-zhanyan}{linkedin.com/in/zhu-zhanyan}%
}

% Summary
Data Engineer with software engineering background building scalable, cloud native backend systems.

\section{Experience}
% format: action, accomplishment, results. concise short sentence fragments
% soft-skills: problem-solving, analytical, communication, teamwork, self-directed
\experience{Admin Support Assistant}{Singapore Armed Forces}{May 2021}{May 2023}
\begin{itemize}
  % skills: PowerBI, ETL, Data Visualisation, Data Analysis?
  % soft-skills: problem-solving, analytical, self-driven
  \item Automated employee well-being interviews as part of self-driven project by
    building a PowerBI Dashboard with a PowerQuery M ETL \& DAX formulas. Saved man hours
    in manual interview tracking in Excel \& drove interview lapses down below KPI targets.

  % skills: PowerBI, DAX, PowerQuery
  % soft-skills: problem-solving, self-driven
  \item Implemented ORD Transcript Templater with MS Access, VBA \& SQL to as part
    of a self-driven initiative to streamline the prior copy \& pasting workflow.
    Templater was instrumental in helping 1 clerk to cope with spike of $\sim$ 
    70 transcripts requested in Nov 2021.

  % skills: Qliksense, Data Analysis, Data Visualisation
  % soft-skills: communication
  \item Performed data analysis \& on an internal Call Center dataset with
    with Qliksense. Made recommendations in Call Center vendor monitoring 
    conveyed in a presentation with Data Storytelling techniques.
\end{itemize}

\experience{ML Engineer Intern}{Gojek}{Mar 2020}{Oct 2020}
\begin{itemize}
  % skills: Software Engineering, Security, ODIC, Java, Golang, Performanace
  \item Made 43 contributions \footnote{https://github.com/feast-dev/feast/commits?author=mrzzy} 
    to the Feast open source project, including ODIC based access control to the Feast's Java 
    \& Golang SDKs, enhancing data security without latency penalty on critical paths.

  % skills: Redis, Protobuf
  % soft-skills: problem-solving, analytical
  \item Identified root cause of decoding error when with serving data from Redis.
    Fixed issue by replacing Protobuf position-based encoding with key-based encoding
    \footnote{https://github.com/feast-dev/feast/pull/908}.

  % skills: Prometheus, Data Quality, DevOps
  % soft-skills: teamwork
  \item Created tool to generate Prometheus Alerts to monitor Data Quality,
    allowing Data Scientists focus on ML instead of DevOps.

  % skills: Data Visualisation, Grafana, BigQuery, SQL
  % soft-skills: teamwork
  \item Visualised Feast usage metrics queried BigQuery Data Warehouse with SQL 
    in a Grafana dashboard. Aided the project manager \& technical leads in their decision making.

  % soft-skills: leadership, teamwork
  \item Advocated for API stability so that dependent applications do not constantly
    have to reworked, freeing up engineering time from patching incompatibility issues.
\end{itemize}

\experience{Software Engineer Intern}{Tinkertanker}{Jan 2018}{Apr 2018}
\begin{itemize}
  % skills: Software Engineering
  \item Developed Tinkertanker's internal employee allocation system with 
    Python, Django \& PostgreSQL that replaced prior Google Sheets system 
    which had performance issues.
  % skills: GitHub Actions, CI/CD, SOftware Testing, Docker, Containers
  \item Wrote GitHub Actions CI/CD pipeline to continuous lint, test codebase
    \& build docker containers to accelerate deployment.
  % skills: Refactoring
  \item Refactored code using SOLID principles to cut through techdebt that
    bogged down developer productivity.
\end{itemize}

\section{Projects}
% skills: airflow, cloud computing, distributed computing, Ray, ML, System Design
\project{Sortin Hat}{github.com/mrzzy/sortin-hat}
\begin{itemize}
  \item Implemented an Airflow ML Pipeline that's trains models to predict student scores
    to facilitate academic target setting.
  \item Wrote Pandas ETL to clean \& transform Excel sheets into ML model features.
  \item Parallelised hyperparameter tuning on distributed Ray Cluster provisioned on-demand.
  \item Designed cloud native architecture with Kubernetes (GKE) \& Object Storage (GCS).
\end{itemize}

% skills: ansible, terraform, vagrant, packer, GCP, DevOps
\project{WARP}{github.com/mrzzy/warp}
\begin{itemize}
  \item Created a web or SSH accessible development environment in a GCP VM,
    built with Terraform, Ansible, Vagrant, Packer.
  \item Ansible playbook provides a single source of truth of tools \& their versions,
    enforcing consistency between WARP VM \& Laptop, allowing for reproduceable code builds.
  \item Automated dependency upgrades with Renovate.
\end{itemize}
  
\section{Education}
\experience{Diploma in Information Technology}{Ngee Ann Polytechnic}{Apr 2018}{Apr 2021}
\begin{itemize}
  \item SGD Scholarship recipient (2018). GPA: 3.82.
  \item Organized workshops on ML and Cloud Computing for 20 pax in tech-interest club.
\end{itemize}

\section{Skills}
\begin{description}
  \footnotesize{
  \item[Technical] Python, SQL, Java, Golang, GCP, BigQuery, AWS, S3, Spark, DBT, Airflow, Kubernetes, Docker, Pandas, Data Modeling, Kimball, Data Visualisation, Data Analysis, Data Quality, Data Warehouse, Data Lake, ETL, Software Enginering, TDD, FP, OOP, Redis, PostgreSQL
  \item[People]
    Self Driven, Self Starter, Problem Solving, Analytical, Team Player, Ambitious, Curious, Result Oriented
  }
\end{description}
